Implicit yaddayadda

### 2011-10-21 papers/PLDI2012/implicitization.tex
graphique resultats
experiments

\usepackage{amsmath}
\usepackage{mathcomp,amsfonts,amssymb,MnSymbol}
\usepackage{dmnatbib}
\usepackage[mathscr]{euscript}
\usepackage{algorithmic,algorithm}

@@

>>>>

\usepackage{amsmath}
\usepackage{mathcomp,amsfonts,amssymb,MnSymbol}
\usepackage{dmnatbib}
\usepackage[mathscr]{euscript}
\usepackage{algorithmic,algorithm}
%\usepackage{graphicx}
%\usepackage{color}

@@

\begin{figure}[h]
  \begin{center}
    \input{./techniques.tex}
  \end{center} 
  \vspace{-20px}
  \caption{Comparison of the abstract values obtained by classical abstract
  interpretation (S), \emph{Guided Static
  Analysis} (G), \emph{Path-focused} technique (PF), our combined technique
  (G+PF), and its version with disjunctive invariants (DIS).}
  \label{fig:techniques}
\end {figure}

\JH{La comparaison DIS/G+PF n'est pas encore correcte (DIS pas compl\`etement
impl\'ement\'e)\\} 
Figures \ref{fig:techniques} shows the results of various comparisons between
the different analysis techniques.
